Paper 1 Analysis

### 2015-10-19 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Now creating rho table.

>>>>

<<delta_table, results="asis">>=
data_delta_table <- 
  table_data %>% 
  filter(Model=="CES") %>% 
  select(Country, Model, CSP, flavor, Energy, Nest, delta_1, delta) %>%
  plyr::rename(c("flavor" = "Factors of prod.",
                  "scale" = "$\\theta$",
                  "lambda" = "$\\lambda$",
                  "delta_1" = "$\\delta_1$",
                  "delta" = "$\\delta$"))

myXTable(data_delta_table,
         caption="Distribution parameters ($\\delta_1$ and $\\delta$) for all modeling choices.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=c(1,1,1,1,1,1,1, 3, 3)
         )
@

<<rho_table, results="asis">>=
data_rho_table <- 
  table_data %>% 
  filter(Model=="CES") %>% 
  select(Country, Model, CSP, flavor, Energy, Nest, rho_1, rho) %>%
  plyr::rename(c("flavor" = "Factors of prod.",
                  "scale" = "$\\theta$",
                  "lambda" = "$\\lambda$",
                  "rho_1" = "$\\rho_1$",
                  "rho" = "$\\rho$"))

myXTable(data_rho_table,
         caption="Values of ($\\rho_1$ and $\\rho$) for all modeling choices.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=c(1,1,1,1,1,1,1, 3, 3)
         )
@
